Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-01 icdm/submission/includes/discussion.tex
added discussion without subsection challenges

\begin{figure}[h]
\centering
\includegraphics[scale=0.45]{images/gensim_vs_adam}
\caption{Convergence time of SGD and Adam compared to Gensim}
\label{fig:gensim_vs_adam}
\end{figure}\subsection{Challenges faced}
During our implementation we did encounter some problems, this subsection has the purpose of preventing the scientific community from making the same mistakes.
\subsubsection{Using the wrong embeddings}
To start with, we did not choose the same initialization value as Gensim in our word embeddings. We initialized the projection layer with a normal distribution between (-1,1), as opposed to Gensim which initializes all the weights to 0. The reason for this, is that at the beginning of our experiments we did not achieve good results with the same initialization as Gensim. Retrospectively we accord this to a learning rate that was too low. After a few simulations, we saw that we did not perform as good as Gensim. And as we changed the initialization of the projection layer back to 0, and already had adjusted the learning rate, we achieved good results. Therefore, this is a recommendation to future work to not set the initialization to (-1,1).

\subsubsection{Batch size and loss function adjustements}\label{ssec:bs_lf}
During our experiments, we faced a moment where we needed to us a very high learning rate (50) to achieve good results. As this is the complete opposite of what is standard we made a few changes to remedy the problem.\\
First, we needed to find a good batch size. During the above-explained raise of the learning rate, we used a batch size of 5000. We then decided to take a batch size of 2000.\\
Secondly, at the same time, we did experiment with different loss functions. As our batched model does not have exactly the same loss function as introduced by Mikolov et al. \cite{mikolov}, we needed to find one that suited our goals the best. At the beginning of our experiment, we took the average of all the scores stored in our final matrix, as explained in \ref{ssec:b_SGM}. But then chose to take the sum as the training did not seem optimal.\\
With these two changes, we did increase convergence time and word similarity, while at the same time having a usual learning rate. \\
Know the question arises why this happened? Is this because of the shape of the loss function better suits our advanced optimizers? Or because the loss function is closer to its original form? Our hypothesis looks the following way:
When taking the average, our loss function is represented as follows:
\begin{equation}
\frac{-1}{b }* \sum_{x\in X} loss(x)
\end{equation}
where $X$ is our batch and $b = |X|$.
When taking the partial derivative of each parameter, the constant $ \frac{-1}{b }$ will remain the same. Therefore, it's the same as taking the sum as the loss function and multiplying each gradient with $\frac{-1}{b }$. As our batch size was really high, i.e 2000 and 5000, this could highly influence the learning rate. This is also the conclusion of Goyal et al. \cite{fb}, that worked with very high batch sizes, i.e 8000: "When the minibatch size is multiplied by k, multiply the learning rate by k".

>>>>

\begin{figure}[h]
\centering
\includegraphics[scale=0.3]{images/gensim_vs_adam}
\caption{Convergence time of SGD and Adam compared to Gensim}
\label{fig:gensim_vs_adam}
\end{figure}
